Titulo

### 2015-02-11 RotacionOutFlows/Paper/ms.tex
more references

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Ostlin14} with the aim of  
exploring the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
line is redshifted into the optical regime. With the outcoming of new and powerfull telescopes
such as the James Webb Space Telescope new LAEs are going to be discovered.

A variety of Astrophysical problems can be studied using LAEs; clustering
of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
properties and cosmological reionization for a recent review see \cite{review} 
among others. This motivates to study in 
detail the processes that model the morphology of the \lya line.

To fully understand the observed spectra of LAEs this galaxies must be modeled.
However the resonant nature of the lines makes this a challenging task. 
Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
\cite{Neufeld90}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
in large scale simulations, while some others have studied detailed galaxies. 
Radiative transfer codes have been used in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.

>>>>

\cite{PartridgePeebles} predicted a population of galaxies with a strong 
Lyman Alpha (\lya) emission,  nowadays galaxies who are selected using the \lya 
line are known as Lyman Alpha Emitters (LAEs). Since the first 
observed LAE by \cite{DjorgovskiThompson} different teams have 
observed several LAEs \cite{Kulas12, Yamada2012, Chonis2013,Finkelstein2013,Ostlin14} with the aim of  
exploring the extragalactic Universe $cite{}$.  Specially at $z>=2$ since it is when the 
line is redshifted into the optical regime. With the outcoming of new and powerfull telescopes
such as the James Webb Space Telescope new LAEs are going to be discovered.

A variety of Astrophysical problems can be studied using LAEs; clustering \citep{Behrens13}
of galaxies at high redshift, Interstellar (ISM) and intergalactic (IGM) medium 
properties \citep{DijkstraKramer} and cosmological reionization for a recent review see \cite{review} 
among others. This motivates to study in 
detail the processes that model the morphology of the \lya line.

To fully understand the observed spectra of LAEs this galaxies must be modeled.
However the resonant nature of the lines makes this a challenging task. 
Analytical solutions for the outcoming spectra in simple ISM static geometries have been dereived
\cite{Adams72, Harrington73, Neufeld90, Dijkstra06}. Recent hydrodynamical simulations have studied the outcomming spectra of LAEs
in large scale simulations, while some others have studied detailed galaxies \citep{Verhamme12}. 
Radiative transfer codes \citep{Laursen09, Verhamme06, CLARA}have been used in order to understand the effect of the 
gas kinematics in the Line, special attention have been devoted to model the presence 
of outflows in the galaxy. here different models have attempt to (name the models, shell cavities etc.)
\citep{Behrens2014}
. Most recently \cite{Garavito14} have studied in detail the effect 
of rotation on the lyman alpha line.
